### 2016-01-20 paper.tex
Blockage ratio is slightly lower

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine due to the lower rotor drag coefficient
and blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is relatively
weaker, which is likely an effect of the RM2's smaller blade chord length and
tapered blades.

>>>>

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine due to the lower rotor drag coefficient
and a slightly blockage ratio \cite{Bachant2015-JoT}. Tip vortex shedding is
relatively weaker, which is likely an effect of the RM2's smaller blade chord
length and tapered blades.
